Presentation Title

### 2017-08-13 paper/s3-system.tex
Write intro
Write paper

\section{System Architecture}

Our system consists of three protocols---the consensus protocol, the transaction protocol and the validation protocol.
It is based on our prior work on TrustChain~\cite{multichain},
where every node independently interacts with each other via their own blockchain\footnote{It is originally called MultiChain but the name has changed to TrustChain}.

\subsection{Overview and intuition}
Unlike most blockchain systems, we do not use a global ledger.
Instead, every node has their own hash chain.
The nodes only store transactions (TX) that they are involved in on their hash chain.
We introduce a special block called checkpoint (CP) block, which represents the state of a hash chain.
The data structure is called Extended TrustChain, a visualisation can be seen on~\Cref{fig:trustchain-good-cp}.
\begin{figure}[h]
\centering
\includegraphics[width=\linewidth]{trustchain-good-cp}
\caption{Visualisation of the Extended TrustChain. $t_{u, i}$ represents a TX block on $u$'s chain with a sequence number of $i$.
$c_{v, j}$ represents a CP block on $v$'s chain with a sequence number of $j$.}
\label{fig:trustchain-good-cp}
\end{figure}

We randomly elect special nodes called facilitators in every round.
The facilitators reach consensus on CP blocks and the consensus result is essentially a set of CP blocks of from (nearly) all the nodes.
While this gives us consensus on a representation of the global state, it does not imply consensus on transactions.
To this end, we introduce the validation protocol that allows any nodes to challenge any other node to produce a set of TX blocks that computes to the CP block in consensus.
Hence we implicitly achieve consensus on transactions.

\subsection{Model and assumptions}
\label{sec:model-assumptions}

We assume purely asynchronous channels with eventual delivery.
Thus in no stage of our protocol do we make timing assumptions.
The adversary has full control of the delivery schedule and the message ordering of all messages.
But they are not allowed to drop messages except for their own\footnote{
    Reliability can be achieved in unreliable networks by resending messages or using some error correction code.
}.
Further, we assume there exists a Public Key Infrastructure (PKI),
and nodes are identified by their unique and permanent public key.

% TODO big N does not follow our convention
In our model, we consider $N$ nodes, which is the population size.
$n$ of them are facilitators, $t$ out of $n$ are malicious and the inequality
$n \ge 3t + 1$ must hold.
This is from the work of Pease, Shostak and Lamport, where they show a network of $n$ nodes cannot reach Byzantine agreement with $t \ge n/3$~\cite{pease1980reaching}.
Further, the inequality $N \ge n + t$ must also hold.
This is due to our system design, which becomes clear in~\Cref{sec:consensus-phase}.

Our threat model is as follows. 
We use a restricted version of the adaptive corruption model.
The first restriction is that corrupted node can only change across rounds.
That is, if a round has started, the corrupted nodes cannot change until the next round.
The second restriction is that the adversary, presumably controlling all the corrupted nodes, is forgetful.
Namely, the adversary may learn the internal state such as the private key of a corrupted node,
but if the node recovers, then the adversary must forget the private key.
This is realistic because otherwise the adversary can eventually learn all the private keys and sabotage the system.

\subsection{Extended TrustChain}
The primary data structure used in our system is the Extended TrustChain.
Each node $u$ has a public and private key pair---$pk_u$ and $sk_u$, and a chain $B_u$.
The chain consist of blocks $B_u = \{ b_{u, i} : i \in \{ 0, \dots, h - 1 \} \}$,
where $b_{u, i}$ is the $i$th block of $u$,
and $h$ is the height of the block (i.e. $h = |B_u|$).
We often use $b_{u, h}$ to denote the latest block.
There are two types of blocks, TX blocks and CP blocks.
If $T_u$ is the set of all TX blocks in $B_u$ and $C_u$ is the set of all CP blocks is $B_u$,
then it must be the case that $T_u \cup C_u = B_u$ and $T_u \cap C_u = \varnothing$.
The notation $b_{u, i}$ is generic over the block type.
We assume there exists a function $\textsf{typeof}: B_u \rightarrow \{ \tau, \gamma \}$ that returns the type of the block,
where $\tau$ represents the TX type and $\gamma$ represents the CP type.

@@

The TX block is a six-tuple, i.e
$$t_{u, i} = \langle \textsf{H}(b_{u, i - 1}), seq_u, txid, pk_v, m, sig_u \rangle.$$
We describe each item in turn.
\begin{enumerate}
\item $\textsf{H}(b_{u, i - 1})$ is the hash pointer to the previous block.
\item $seq_u$ is the sequence number which should equal $i$.
\item $txid$ is the transaction identifier, it should be generated using a cryptographically secure pseudo-random number generator by the initiator of the transaction.
\item $pk_v$ is the public key of the counterparty $v$.
\item $m$ is the transaction message.
\item $sig_u$ is the signature created using $sk_u$ on the concatenation of the binary representation of the five items above.
\end{enumerate}
The fact that we have no constraint on the content of $m$ is in alignment with our design goal---application neutrality.

@@

Our consensus protocol runs in rounds.
Every round is identified by a round number $r$, which is incremented on every new round.
The consensus result is a tuple, i.e. $\C_r = \langle r, C \rangle$,
where $C$ is a set of CP blocks agreed by the facilitators of round $r$.
\end{definition}

@@

\subsection{Consensus Protocol}
Our scalable consensus protocol runs on top of Extended TrustChain.
It uses an unmodified asynchronous subset consensus (ACS) algorithm as the key building block.
The objectives of the protocol are to
    allow honest nodes always make progress (in the form of creating new CP blocks),
    compute correct consensus result in every round
    and have an unbiased election of facilitators.
Concretely, we define the necessary properties as follows.
\begin{definition}
\label{def:consensus}
\textbf{\emph{Properties of the consensus protocol}}

$\forall r \in \mathbb{N}$, the following properties must hold.
\begin{enumerate}
    \item \emph{Agreement}:
        If one correct node outputs a set of facilitators $\F_r$,
        then every node outputs $\F_r$
    \item \emph{Validity}:
        If any correct node outputs $\F_r$, then 
            \begin{enumerate}
                \item $|\C_r| \ge N - t$ and each CP in $\C_r$ belong to a different node\footnote{
                $\C_r$ is a tuple but we abuse the notation here by writing $|\C_r|$ to mean the number of CP blocks in the second element of $\C_r$.}.
                \item $\F_r$ must contain at least $n - t$ honest nodes and
                \item $|\F_r| = n$.
            \end{enumerate}
    \item \emph{Fairness}:
        Every node with a CP block in $\C_r$ should have an equal probability of becoming a member of $\F_r$.
    \item \emph{Termination}:
        Every correct node eventually outputs some $\F_r$.
\end{enumerate}
\end{definition}
These properties are similar to Byzantine consensus properties but there are subtle differences.
Firstly, they are properties for every node in the network and not just the facilitators.
Secondly, they must be satisfied for all rounds because the whole system falls apart if one of the property cannot be satisfied in one of the rounds.

@@

In practice, the bootstrap oracle is most likely the software developer and some of the desired properties cannot be achieved.
In particular, it is not possible to have the fairness property because it is unlikely that the developer knows the identity of every node in advance.

@@

The core of the consensus phase is the ACS protocol.
While any ACS protocol that satisfies the standard definition will work,
we use a simplification of HoneyBadgerBFT~\cite{miller2016honey} as our ACS protocol
because it is a consensus algorithm designed for blockchain systems.
We do not use the full HoneyBadgerBFT due to the following.
First, the transactions in HoneyBadgerBFT are first queued in a buffer and the main consensus algorithm starts only when the buffer reaches an optimal size.
We do not have an infinite stream of CP blocks, thus buffering is unsuitable.
Second, HoneyBadgerBFT uses threshold encryption to hide the content of the transactions.
But we do not reach consensus on transactions, only CP blocks, so hiding CP blocks is meaningless for us as it contains no transaction information.

@@

Upon receiving $\C_{r + 1}$ and at least $n - f$ valid signatures by some node $u$, $u$ performs two tasks.
First, it creates a new CP block using $\textsf{new\_cp}(\C_{r + 1}, r + 1)$ using \Cref{alg:new-cp}.
Second, it computes the new facilitators using $\textsf{get\_facilitator}(\C_{r + 1}, n)$ using \Cref{alg:facilitator},
and updates its facilitator set to the result.
This concludes the consensus phase and brings us back to the beginning of the consensus phase.

@@

Our protocol has some similarities with synchronizers~\cite[Chapter 10]{podc} because it is effectively a technique to introduce synchrony in an asynchronous environment.
If we consider the facilitators as a collective authority, then it can be seen as a synchronizer that sends pulse messages (in the form of \texttt{cons\_msg} and \texttt{cons\_sig}) to indicate the start of a new clock pulse.
Every node then sends a completion messages (in the form of \texttt{cp\_msg}) to the new collective authority to indicate that they are ready for the next pulse.

@@

The TX protocol, shown in \Cref{alg:tx-proto}, is run by all nodes.
It is also known as True Halves, first described by Veldhuisen~\cite[Chapter~3.2]{truehalves}.
Nodes that wish to initiate a transaction calls $\textsf{new\_tx}(pk_v, m, txid)$ (\Cref{alg:new-tx}) with the intended counterparty $v$ identified by $pk_v$ and message $m$.
$txid$ should be a uniformly distributed random value, i.e. $txid \in_R \{0, 1\}^{256}$.
Then the initiator sends $\langle \texttt{tx\_req}, t_{u, h}\rangle$ to $v$.

@@

A key feature of the TX protocol is that it is non-blocking.
At no time in \Cref{alg:new-tx} or \Cref{alg:tx-proto} do we need to hold the chain state and wait for some message to be delivered before committing a new block to the chain.
This allows for high concurrency where we can call $\textsf{new\_tx}(\cdot)$ multiple times without waiting for the corresponding \texttt{tx\_resp} messages.

@@

\subsubsection{Validity definition}
A transaction can be in one of three states in terms of validity---\emph{valid}, \emph{invalid} and \emph{unknown}.
Given a fragment $F_{v, j}$, the validity of the TX block $t_{u, i}$ and the agreed fragment of it is captured by the function $\textsf{get\_validity}(t_{u, i}, F_{u, i}, F_{v, j})$ (\Cref{alg:get-validity}).
Note that $t_{u, i}$ and $F_{u, i}$ are assumed to be valid,
otherwise the node calling the function would have no point of reference.
This is not difficult to achieve.
Typically the caller is $u$, so it knows its own TX block and the corresponding agreed fragment.
If the caller is not $u$, it can always query for the agreed fragment that contains the transaction of interest from $u$.

\Cref{alg:get-validity} works as follows.
Before~\Cref{line:valid-fragment},
we essentially check whether the fragment is the one that the verifier needs.
If it is not, then the verifier cannot make any decision and return \emph{unknown}.
This is likely to be the case for new transactions because the result of $\textsf{agreed\_fragment}(\cdot)$ would be $\bot$.
The next two conditions check for tampering or missing blocks, if any of these misconducts are detected, then the TX is invalid.

@@

Further, the caller of $\textsf{get\_validity}(t_{u, i}, F_{u, i}, F_{v, j})$ is not necessarily 
$u$\footnote{In practice, it often is because after completing the TX protocol the parties are incentivised to check that the counterparty ``did the right thing''.}
Any node $w$ may call $\textsf{get\_validity}(t_u{u, i}, F_{u, i}, F_{v, j})$ as long as $w$ has an the necessary input parameters.
$F_{u, i}$  and $t_{u, i}$ may be readily available if $w = u$.
Otherwise, $w$ could query $u$ with the \texttt{vd\_req} message and then obtain the result from \texttt{vd\_resp}.
This is the validation protocol which we describe next.

@@

\subsection{Design variations and tradeoffs}
\label{sec:tradeoffs}

Up to this point,
we have discussed our protocol in the context of the model and assumptions defined in \Cref{sec:model-assumptions}.
In this section, 
we explore a few design variations which we can make, some of them require a relaxed version of our original model.
They enable better performance, allow us to apply our design in the fully permissionless setting and improves privacy.

\subsubsection{Using timing assumption in the permissionless setting}
\label{sec:permissionless}
Our model is purely asynchronous, where we make no timing assumptions anywhere in the protocol.
However, in many applications it is often fine to make timing assumptions.
For example, TCP relies on timeout for its retransmission and the \texttt{nLockTime} property in Bitcoin transactions makes the transaction unspendable until some time in the future (either Unix time or block height)~\cite{bitcoindevguide}.
One limitation of our system is that we use the parameter $N$ in our algorithms, which makes it unsuitable for the permissionless environment where users can join and leave at will.
In this section we show how making a timing assumption would allow us to operate in the permissionless setting.

At the start of our consensus phase (\Cref{sec:consensus-phase}), facilitators must wait for $N-f$ \texttt{cp\_msg} messages.
This is the only place where we used $N$ as a parameter.
To introduce timing, instead of waiting for $N-f$ messages, we wait for some time $D$,
such that $D$ is sufficiently long for honest nodes to send their CP blocks to the facilitators.
Consequently, this removes the need for a PKI because the collected CP blocks may be from nodes that nobody has seen in the past.
However, choosing the parameter $D$ is difficult and depends on a number of factors such as the network condition, message size, and so on.
Overestimating it would make agreed fragments much longer than usual, which increases communication costs for validation.
Underestimating it would lead to unfairness where users with a poor internet connection will have a lower chance to be selected as a facilitator in the next round.
Nevertheless, there is a significant gain for making the timing assumption and that is the ability to operate in the permissionless setting which we explain next.

Suppose a new node wish to join the network and the facilitators are known (this can be done with a public registry).
It simply sends its latest CP block to the facilitators.
Then, in the next round, the node will have a chance to become a facilitator just like any existing node.
To leave the network, nodes simply stop submitting CP blocks.
There is a subtlety here which happens when the node is elected as a facilitator in the following round.
In this case, the node must fulfil its obligation by completing the consensus protocol, but without proposing its own CP block, before leaving.
Otherwise, the $n \ge 3t + 1$ condition may be violated.

\subsubsection{Privacy preserving validation protocol using compact blocks}
\label{sec:compact}
Our approach already has privacy preserving features in comparison to early blockchain systems.
That is, the transactions for each node are only revealed during the validation protocol.
Hence if two nodes never directly or indirectly interact with each other,
their transactions are never revealed.

We can take our privacy-preserving property one step further by introducing another level of hash pointer indirection.
The result is shown in~\Cref{fig:compact}.
\begin{figure}
    \includegraphics[width=0.7\linewidth]{compact}
    \centering
    \caption{The chain on the left represent direct chaining, where the digest in ``Prev'' is simply the digest of the previous block.
    The chain on the right uses compact blocks, represented by the smaller squares.
    Compact blocks also form a chain as before, but they each have a hash pointer to the full block, identified by ``Seq'' and ``Digest''.}
    \label{fig:compact}
\end{figure}

Concretely, we introduce an additional block type,
namely compact block.
Such blocks only have three attributes,
\begin{enumerate}
\item Seq---the sequence number its corresponding block,
\item Digest---the digest of its corresponding block, and
\item Prev---the digest of the previous compact block.
\end{enumerate}
Each compact block has a corresponding full block (either a CP block or a TX block).
The relationship is uniquely identified with Seq or Digest.
Recall that our original validation protocol requires the nodes to send the full agreed fragment.
With compact blocks, it is only necessary to send the compact version of the agreed fragment.
The validation then proceeds in a similar fashion,
provided that the pair of the to-be-validated TX block is known.

\subsubsection{Optimising validation protocol using cached agreed fragments}
\label{sec:caching}
One more way to improve the efficiency of the validation protocol is to use a single agreed fragment to validate multiple transactions.
Concretely, upon receiving an agreed fragment from node $A$,
rather than validating a single transaction,
we attempt to validate all transactions with $A$ in the unknown state in that fragment.

For a node, the benefit of this technique is maximised when it only transacts with one other node.
In this case, the communication of one fragment is sufficient to validate all transactions in that fragment.
In the opposite extreme, if every transaction that the node makes is with another unique node,
then the caching mechanism would have no effect.

\subsubsection{Global fork detection}
The validation algorithm guarantees that there are no forks within a single agreed fragment.
This is sufficient for some applications such as proving the existence of some information.
However, for applications such as digital cash where every block depends on one or more previous blocks,
our scheme is not suitable.
For such applications, we need to guarantee that there are no forks from the genesis block leading up to the TX block of interest.

There are a variety of approaches to do global fork detection.
First and the easiest solution is to simply ask for the complete chain of the counterparty.
The verifier can be sure that there are no forks if the following holds.
\begin{enumerate}
    \item The hash pointers are correct.
    \item All the CP blocks are in consensus.
    \item The TX of interest is in the chian.
\end{enumerate}
We use this approach in our prior work on Implicit Consensus~\cite{implicitconsensus}.
It may sound inefficient at first, but nodes employ caching to minimise communication costs.

>>>>

\section{System Architecture}
\label{sec:system}

To describe our system, we first give an informal overview and then move on to the formal description.
Unlike most blockchain systems, we do not use a global ledger.
Instead, every node has their own hash chain.
The nodes only store transactions (TX) that they are involved in on their hash chain.
Transactions are stored in TX blocks and every block only contains one transaction.
We introduce a special block called checkpoint (CP) block, which represents the state of a hash chain.
Such data structure is called Extended TrustChain,
a visualisation can be seen on~\Cref{fig:trustchain-good-cp}.
\begin{figure}[h]
\centering
\includegraphics[width=\linewidth]{trustchain-good-cp}
\caption{Visualisation of the Extended TrustChain. $t_{u, i}$ represents a TX block on $u$'s chain with a sequence number of $i$.
$c_{v, j}$ represents a CP block on $v$'s chain with a sequence number of $j$.}
\label{fig:trustchain-good-cp}
\end{figure}

We randomly elect $n$ special nodes called facilitators in every round.
The facilitators reach consensus on CP blocks using an existing consensus algorithm---asynchronous subset consensus from HoneyBadgerBFT~\cite{miller2016honey}.
The consensus result is essentially a set of CP blocks from (nearly) all the nodes.
While this gives us consensus on a representation of the global state, it does not imply consensus on transactions.
To this end, we introduce a validation protocol that allows any nodes to challenge any other node to produce a set of TX blocks that computes to the CP block in consensus.
Hence we implicitly achieve consensus on transactions.
Since the transaction and validation protocols only make point-to-point communication,
we achieve horizontal scalability.

The formal description is given next,
it consist of one data structure---Extended TrustChain,
and three protocols---consensus protocol, transaction protocol and validation protocol.

\subsection{Extended TrustChain}
Each node $u$ has a public and private key pair---$pk_u$ and $sk_u$, and a chain $B_u$.
The chain consist of blocks $B_u = \{ b_{u, i} : i \in \{ 0, \dots, h - 1 \} \}$,
where $b_{u, i}$ is the $i$th block of $u$,
and $h$ is the height of the block (i.e. $h = |B_u|$).
We often use $b_{u, h}$ to denote the latest block.
There are two types of blocks, TX blocks and CP blocks.
If $T_u$ is the set of all TX blocks in $B_u$ and $C_u$ is the set of all CP blocks is $B_u$,
then it must be the case that $T_u \cup C_u = B_u$ and $T_u \cap C_u = \varnothing$.
The notation $b_{u, i}$ is generic over the block type.
We assume there exists a function $\textsf{typeof}: B_u \rightarrow \{ \tau, \gamma \}$ that returns the type of the block,
where $\tau$ represents the TX type and $\gamma$ represents the CP type.

@@

The TX block is a six-tuple, i.e
$$t_{u, i} = \langle \textsf{H}(b_{u, i - 1}), seq_u, txid, pk_v, m, sig_u \rangle.$$
We describe each item in turn.
\begin{enumerate}
\item $\textsf{H}(b_{u, i - 1})$ is the hash pointer to the previous block.
\item $seq_u$ is the sequence number which should equal $i$.
\item $txid$ is the transaction identifier, it should be generated using a cryptographically secure pseudo-random number generator by the initiator of the transaction.
\item $pk_v$ is the public key of the counterparty $v$.
\item $m$ is the transaction message.
\item $sig_u$ is the signature created using $sk_u$ on the concatenation of the binary representation of the five items above.
\end{enumerate}
The fact that we have no constraint on the content of $m$ is in alignment with our problem description---application neutrality.

@@

Our consensus protocol runs in rounds.
Every round is identified by a round number $r$, which is incremented on every new round.
The consensus result is a tuple, i.e.
$$\C_r = \langle r, C \rangle,$$
where $C$ is a set of CP blocks agreed by the facilitators of round $r$.
\end{definition}

@@

\subsection{Consensus Protocol}
Our scalable consensus protocol runs on top of Extended TrustChain.
It uses an unmodified asynchronous subset consensus (ACS) algorithm as the key building block (we describe the reasoning later).
The objectives of the protocol are to
allow honest nodes always make progress (in the form of creating new CP blocks),
compute correct consensus result in every round
and have an unbiased election of facilitators.
Concretely, we define the necessary properties as follows.
\begin{definition}
\label{def:consensus}
\textbf{\emph{Properties of the consensus protocol}}

$\forall r \in \mathbb{N}$, the following properties must hold.
\begin{enumerate}
    \item \emph{Agreement}:
        If one correct node outputs a set of facilitators $\F_r$,
        then every node outputs $\F_r$
    \item \emph{Validity}:
        If any correct node outputs $\F_r$, then 
            \begin{enumerate}
                \item $|\C_r| \ge N - t$ and each CP in $\C_r$ belong to a different node\footnote{
                $\C_r$ is a tuple but we abuse the notation here by writing $|\C_r|$ to mean the number of CP blocks in the second element of $\C_r$.}.
                \item $\F_r$ must contain at least $n - t$ honest nodes and
                \item $|\F_r| = n$.
            \end{enumerate}
    \item \emph{Termination}:
        Every correct node eventually outputs some $\F_r$.
    \item \emph{Fairness}:
        Every node with a CP block in $\C_r$ should have an equal probability of becoming a member of $\F_r$.
\end{enumerate}
\end{definition}
These properties are similar to Byzantine consensus properties but there are subtle differences.
Firstly, they are properties for every node in the network and not just the facilitators.
Secondly, they must be satisfied for all rounds,
because a failure in one round will lead to failures in sebsequent rounds.

@@

@@

The core of the consensus phase is the ACS protocol,
it is based on the construction described in HoneyBadgerBFT~\cite{miller2016honey}.
We do not use the full HoneyBadgerBFT due to the following.
First, the transactions in HoneyBadgerBFT are first queued in a buffer and the main consensus algorithm starts only when the buffer reaches an optimal size.
We do not have an infinite stream of CP blocks, thus buffering is unsuitable.
Second, HoneyBadgerBFT uses threshold encryption to hide the content of the transactions.
But we do not reach consensus on transactions, only CP blocks, so hiding CP blocks is meaningless for us as it contains no transaction information.

@@

Upon receiving $\C_{r + 1}$ and at least $n - f$ valid signatures by some node $u$, $u$ performs two tasks.
First, it creates a new CP block using $\textsf{new\_cp}(\C_{r + 1}, r + 1)$ using \Cref{alg:new-cp}.
Second, it computes the new facilitators using $\textsf{get\_facilitator}(\C_{r + 1}, n)$ (\Cref{alg:facilitator}),
and updates its facilitator set to the result.
This concludes the consensus phase and brings us back to the state at the beginning of the consensus phase,
so a new round can be started.

@@

@@

The TX protocol, shown in \Cref{alg:tx-proto}, is run by all nodes.
It is also known as True Halves, first described informally by Veldhuisen~\cite[Chapter~3.2]{truehalves}.
Nodes that wish to initiate a transaction calls $\textsf{new\_tx}(pk_v, m, txid)$ (\Cref{alg:new-tx}) with the intended counterparty $v$ identified by $pk_v$ and message $m$.
$txid$ should be a uniformly distributed random value, i.e. $txid \in_R \{0, 1\}^{256}$,
then sends $\langle \texttt{tx\_req}, t_{u, h}\rangle$ to $v$.

@@

A key feature of the TX protocol is that it is non-blocking.
At no time in \Cref{alg:new-tx} or \Cref{alg:tx-proto} do we need to hold the chain state and wait for some message to be delivered before committing a new block to the chain.
This allows for a high level of concurrency where we can call $\textsf{new\_tx}(\cdot)$ multiple times without waiting for the corresponding \texttt{tx\_resp} messages.

@@

\subsubsection{Validity definition}
A transaction can be in one of three states in terms of validity---\emph{valid}, \emph{invalid} and \emph{unknown}.
Given a fragment $F_{v, j}$,
the validity of the TX block $t_{u, i}$ with its corresponding fragment $F_{u, i}$ is captured by the function $\textsf{get\_validity}(t_{u, i}, F_{u, i}, F_{v, j})$ (\Cref{alg:get-validity}).
Note that $t_{u, i}$ and $F_{u, i}$ are assumed to be valid,
otherwise the node calling the function would have no point of reference.
This is not difficult to achieve,
because typically the caller is $u$, so it knows its own TX block and the corresponding agreed fragment.
If the caller is not $u$, it can always query for the agreed fragment that contains the transaction of interest from $u$.

% \Cref{alg:get-validity} works as follows.
% Before~\Cref{line:valid-fragment},
% we essentially check whether the fragment is the one that the verifier needs.
% If it is not, then the verifier cannot make any decision and return \emph{unknown}.
% This is likely to be the case for new transactions because the result of $\textsf{agreed\_fragment}(\cdot)$ would be $\bot$.
% The next two conditions check for tampering or missing blocks, if any of these misconducts are detected, then the TX is invalid.

@@

@@

\subsection{Design variations and tradeoffs}
\label{sec:tradeoffs}
In this section, 
we explore a few design variations which we can make, some of them require a relaxed version of our original model.
They enable better performance and allow us to apply our design in the fully permissionless setting.

\subsubsection{Using timing assumption in the permissionless setting}
\label{sec:permissionless}
One limitation of our system is that we use the parameter $N$ in our algorithms, which makes it unsuitable for the permissionless environment where users can join and leave at will.
In this section we show how making a timing assumption would allow us to operate in the permissionless setting.

At the start of our consensus phase (\Cref{sec:consensus-phase}), facilitators must wait for $N-f$ \texttt{cp\_msg} messages.
This is the only place where we used $N$ as a parameter.
To introduce timing, instead of waiting for $N-f$ messages, we wait for some time $D$,
such that $D$ is sufficiently long for honest nodes to send their CP blocks to the facilitators.
Consequently, this removes the need for a PKI because the collected CP blocks may be from nodes that nobody has seen in the past.

The new protocol handles churn as follows.
Suppose a new node wish to join the network and the facilitators are known (this can be done with a public registry).
It simply sends its latest CP block to the facilitators.
Then, in the next round, the node will have a chance to become a facilitator just like any existing node.
To leave the network, nodes simply stop submitting CP blocks.
There is a subtlety here which happens when the node is elected as a facilitator in the following round.
In this case, the node must fulfil its obligation by completing the consensus protocol, but without proposing its own CP block, before leaving.
Otherwise, the $n \ge 3t + 1$ condition may be violated.

\subsubsection{Optimising validation protocol using cached agreed fragments}
\label{sec:caching}
One more way to improve the efficiency of the validation protocol is to use a single agreed fragment to validate multiple transactions.
Concretely, for node $A$, upon receiving an agreed fragment from node $B$,
rather than validating a single transaction,
$A$ attempts to validate all transactions with performed with $B$ in the unknown state, in that fragment.

The benefit of this technique is maximised when a node only transacts with one other node.
In this case, the communication of one fragment is sufficient to validate all transactions in that fragment.
In the opposite extreme, if every transaction that the node makes is with another unique node,
then the caching mechanism would have no effect.

\subsubsection{Total fork detection}
\label{sec:fork}
The validation algorithm guarantees that there are no forks within a single agreed fragment.
This is sufficient for some applications such as proving the existence of some information.
However, for applications such as digital cash where every block depends on one or more previous blocks,
our scheme is not suitable.
For such applications, we need to guarantee that there are no forks from the genesis block leading up to the TX block of interest.

We offer two approaches to do total fork detection.
First and the easiest solution is to simply ask for the complete chain of the counterparty.
The verifier can be sure that there are no forks if the following holds.
\begin{enumerate}
    \item The hash pointers are correct.
    \item All the CP blocks are in consensus.
    \item The TX of interest is in the chian.
\end{enumerate}
We use this approach in our prior work on Implicit Consensus~\cite{implicitconsensus}.
Nodes employ caching to minimise communication costs, we call this effect spontaneous sharding.

### 2017-08-13 paper/s4-analysis.tex
Write paper

\section{Correctness and fault tolerance analysis}
\label{sec:analysis}
Here we evaluate our system analytically to ensure the desired properties (\Cref{def:consensus} and \Cref{def:validation}) hold.
An informal argument is given in this section, we refer to~\cite{checo}??? for an indepth analysis.

\subsection{Correctness of the consensus protocol}
Recall that the consensus protocol properties (\Cref{def:consensus}) has
four conditions---agreement, validity, fairness and termination.
Agreement, validity and termination hold due to the fact that the following three facts
\begin{enumerate}
    \item The CP blocks sent to the facilitators are eventually delivered and then ACS eventually starts.
    \item Agreement, validity and termination holds for ACS.
    \item The consensus result and signatures are eventually disseminated to all the nodes.
\end{enumerate}

@@

\subsection{Correctness of the validation protocol}
Using the previous result,
we show that the agreement and validity properties (from~\Cref{def:validation}) hold for the validation protocol.

The validty property holds because we use $\textsf{get\_validity}(\cdot)$ in the validation protocol.
The agreement property holds due to the collision resistent property of cryptographically secure hash function.
Suppose two honest nodes decided on two different state, \emph{valid} and \emph{invalid} for the same transaction.
Due to the properties of the consensus protocol, the agreed enclosure for the transaction must be the same.
For that to happen, two agreed fragments must exist for the same transaction.
Recall that blocks form a hash chain.
So this cannot happen unless the hash function is not cryptographically secure.

Liveness, unfortunately does not hold in our model.
A malicious node can ask honestly when running the transaction protocol,
but then never respond to any validation requests.
Therefore there are transactions that can never be validated.
Nevertheless, the malicious node will be at an economical loss if it is not responsive because honest nodes are less likely to make contact with nodes that do not respond to validation messages.

@@

The bound is not tight, but it is useful for picking parameters.
If $n$ is known, then we can pick a $\alpha$ such that the probability becomes small.
On the other hand, if $\alpha$ is fixed, but small, we may increase $n$ to achieve the same.
Furthermore, hypergeometric distributions have light tails with ``faster-than-exponential fall-off''~\cite{skala2013hypergeometric},
the probability for picking more than $\lfloor \frac{n-1}{3} \rfloor$ malicious nodes drops of exponentially as the expected value moves away from $\lfloor \frac{n-1}{3} \rfloor$.
To put this into perspective,
suppose $n = 1000$ and $\alpha = 1/5$, i.e. a fifth of the nodes are malicious.
Then the probability to draw more black balls than the threshold is only $2.6 \times 10^{-16}$.

>>>>

\section{Correctness and fault tolerance analysis}
\label{sec:analysis}
We evaluate our system analytically to ensure the desired properties (\Cref{def:consensus} and \Cref{def:validation}) hold.
An informal argument is given in this section, we refer to~\cite[Chapter 4]{checo}??? for an indepth analysis.

\subsection{Correctness of the consensus protocol}
Recall that the consensus protocol properties (\Cref{def:consensus}) has
four items---agreement, validity, termination and fairness.
The first three hold due to the following facts.
\begin{itemize}
    \item The CP blocks sent to the facilitators are eventually delivered and then ACS eventually starts.
    \item Agreement, validity and termination holds for ACS as they are the properties of ACS and are proven to hold in~\cite{miller2016honey}.
    \item The consensus result and signatures are eventually disseminated to all the nodes,
        so honest nodes must hold the same result as the honest facilitators.
\end{itemize}

@@

\subsection{Correctness of the validation protocol}
\label{sec:correctness-of-validity}
Using the previous result,
we show that the agreement and validity properties (from~\Cref{def:validation}) hold for the validation protocol.

The validty property holds because we use $\textsf{get\_validity}(\cdot)$ in the validation protocol.
The agreement property holds because we model $\textsf{H}(\cdot)$ as a query to a random oracle.
Suppose two honest nodes decided on two different state, \emph{valid} and \emph{invalid} for the same transaction.
Due to the properties of the consensus protocol, the agreed enclosure for the transaction must be the same.
For that to happen, two agreed fragments must exist for the same transaction.
Recall that blocks form a hash chain.
So this cannot happen unless the adversary can compute the inverse of $\textsf{H}(\cdot)$ with high probability.

Liveness, unfortunately does not hold in our model.
A malicious node can ask honestly when running the transaction protocol,
but then never respond to any validation requests.
Therefore there are transactions that can never be validated.
Nevertheless, the malicious node will be at an economical loss if it is not responsive because honest nodes are less likely to make contact with nodes that do not respond to validation requests.

@@

The bound is not tight, but it is useful for picking parameters for a desired level of fault tolerance.
If $n$ is known, then we can pick a $\alpha$ such that the probability becomes small.
On the other hand, if $\alpha$ is fixed, but small, we may increase $n$ to achieve the same.
Furthermore, hypergeometric distributions have light tails with ``faster-than-exponential fall-off''~\cite{skala2013hypergeometric}.
So the probability for picking more than $\lfloor \frac{n-1}{3} \rfloor$ malicious nodes drops of exponentially as the expected value moves away from $\lfloor \frac{n-1}{3} \rfloor$.
To put this into perspective,
suppose $n = 1000$ and $\alpha = 1/5$, i.e. a fifth of the nodes are malicious.
Then the probability to elect more malicious nodes than the threshold is only $2.6 \times 10^{-16}$.
